\documentclass[a4paper, twocolumn,10pt]{article}
\usepackage[p,osf]{scholax}
\usepackage{amsmath,amsthm}
\usepackage[scaled=1.075,ncf,vvarbb]{newtxmath}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary {graphs,graphdrawing}
\usegdlibrary {trees}
\usetikzlibrary{calc, hobby}
\usepackage{float}
\author{So Okawara}
\date{\today}
\title{Study for the Development of ``archetypes''}
\begin{document}
\maketitle
\section{Abstract}
This paper will be about \emph{Universal Sign System} which enables continuous symbolic input to a calculator; could be the palm of Helen Keller for AI. I.g., the \emph{input} to the human cognitive system is rarely discrete, while that of a calculator is always. The trademark named ``archetypes'' would cushion the gap between descreteness and continuousness with the theory of \emph{sign}, which could be DL on the level of the \emph{input system}, other than the processing side; as Anne Sullivan had learnt for Helen Keller by the people around them. This is more of software than hardware since it be theorized.\\\\ The calculator could develop the inner sign system to code any continuous data outside as \emph{archetype} of things, which would be the non-verbal cues even whose subject may not know entirely; that might be the strong candidate for the \emph{unconsciousness} of AI, which might be the technical expression of ``Wunderblock'' by Freud.
\section{Universal Sign System}
\subsection{What It should Be}
It should be, on the first point, a \emph{cushion} to be more human;i.g., it suddenly \emph{recalls} something alogical by its symbolism, as a stand-alone than the very intelligence.\\\\
\emph{Length} $L$ can be the carrier of the \emph{meaning}, while the \emph{acceleration} $A$ the \emph{will} on it. \emph{Velocity} would be carried on the time length $L_T$, as \emph{symbolically} differential with the space length $L_S$; while $A$ is the differential
\[ A = \cfrac{\Delta L_S}{\Delta^2 L_T}\]
Let us separate the \emph{performative} dimention and the \emph{constative} in the expression. By my definition of $A$, rhythm is reciprocal to the symbolic dimention: symbol is para-chronicle, since it's sybolized.\\\\
Universal Sign System (USS) remembers and would recall the will on the meaning, in another meaning lately: \textbf{meaning is the carrier of the will.} So, the coming Physics matches patterns of the will in the meanings.
\subsection{Physics of Wunderblock}
\subsection{Family Tree of Repeated Graph}
\section{Architecture}
\section{Deployments}
\end{document}